\documentclass[11pt]{article}
%Gummi|065|=)
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{bbm}
\usepackage{geometry}
\usepackage{comment}
\geometry{letterpaper, margin=1in}
\title{\textbf{BEM 107: Applied Corporate Finance and Investment Banking}}
\author{Justin Leong}
\date{\today}
\begin{document}

\maketitle

\section{Lecture 1 - 3/31/2016}
What does the Professor do?
\\serve as a finance expert in high stakes financial litigation; BoA Professor of Finance at UCLA, permanent visitor at Caltech; San Marino Business Partners - hedge funds in risky technology companies; (2010 - Cornell Investors)
\\\\Where do companies get a bunch of money to buy securities?
\\Repo(repurchase) - buy security and immediately sell to someone else with the agreement to buy it back the next day at cost + overnight interest rate
\\\\What happens if a bank refuses to participate in repo financing anymore?
\\The company dies
\\\\How did they make money last year?
\\Shorted GoPro because it has low barrier to entry; Bought Apple options since he thought it was overvalued
\\\\Where do values of companies come from?
\\consumable cash; (e.g. dividends or future cash flows)
\\\\What are the benefits of putting a solar panel system on your roof?
\\cash grant, accelerated depreciation(not a company so you don't get it), performance based incentives(based on how much energy you generate - have to fill out a bunch of forms every year); now you just lease solar panels for 90\% of normal Edison energy rate (Sequoia Pacific Solar buys the installations)
\\\\What do you need to write off depreciation?
\\lots of earnings (Google + Solar City = Sequoia Pacific Solar)
\\\\What are the two big disputes in solar?
\\valuation of solar panel systems; net negative customers don't pay to maintain grid
\\\\What is the goal of corporations?
\\to maximize shareholder value
\\\\How do you do it?
\\nobody knows
\\\\What is divestment?
\\don't invest in companies like Exxon Mobil which contribute to climate change
\\\\What does the Caltech Board of Trustees do?
\\fundraise or donate money
\\\\What does the Board of Directors do?
\\fire management
\\\\What do you do if the company isn't maximizing shareholder values?
\\get 50\% of shareholders to choose a board of directors to hire a new management
\\\\How do you do that with Google?
\\you can't because Larry Page and his buddy have Class B shares which have 50 times the voting rights per share
\\\\What is the problem of stationarity?
\\Is the underlying problem itself stable
\\\\What is a superior investor?
\\someone who can generate excess return given a level of risk
\\\\What do financial markets allow?
\\demand to decide what to invest in and allows savers to invest
\\\\What does Yahoo say about the Beta of Tesla?  What does Google say?
\\0.985412; 1.25
\\\\What is goodwill?
\\book value of companies acquired that aren't in their assets
\\\\What doesn't appear on the balance sheet?
\\internally generated technologies(intangible value) such as Google's search technology
\\\\

\begin{description}
\section{Lecture 1 - 3/31/2016}
\item[How much is Snap worth today?]
  20 billion
  started by professor's godson (owns 25\%)
\item[what does the professor do?]
  expert witness on complex financial matters
\item[Why did Professor Cornell get hired as an expert witness?]
  financial institution sold derivative to company and company claimed institution didn't explain risk;
  guys on 26th floor knows (senior executive said bunch of Chinese and Indian guys doing derivatives)
\item[What is needed for the class?]
  bring laptop
\item[What i]
  started in 2008;
  \$5 million to \$31 million;
  write insurance on Berkshire Hathaway (expert witness for Buffett);
  aggressively taking equity;
  Gene Fama referred to investment strategy as ``shit, dumb luck'';
  believes that current state of investment world is terrible
\item[Feynman story]
  mechanical drawing class;
  some joker picked up a French curve and asked whether curves had special formula;
  curve is made that lowest point on each curve was tangent to horizon;
  knowledge is fragile
\item[What does it mean to short?]
  borrow shares and sell them;
  you have to pay dividends
\item[Why do you invest?]
  to get cash
\item[How does valuation work?]
  you put cash in now to an investment and in the future you get more cash out;
  time and risk
\item[What is asset pricing?]
  developing mathematical theories about how assets are priced;
  $P = E(Mx)$;
  X is  the payoff, $X_{t+1}$ is random;
  given a security and probability of payoffs and utility functions, we can figure out how assets will be priced
\item[How much is Amazon's market cap?]
  428 billion;; 898.28 per share;
  only beat by Apple, Google, and Microsoft
\item[What is Feynman's Los Alamos story?]
  asked how would you rate your sense of well being by the government (64);
  psychologist said is that good or bad;
  Feynman asked that is the question
\item[What is the idea of investing?]
  trying to get superior returns based on analysis of a company;
  1. have to disagree with market (otherwise just buy index fund);
  2. be right
  3. market comes to realize you are right
\item[What is Cornell's position on Tesla?]
  short - he thinks it is worth 150
\item[What is the difference between asset pricing and investing?]
  Asset pricing is a math theory that explains how market prices are set.
  Investing is about the business narrative, not the finance model
\item[What is the Snap narrative?]
  young people and their kids will stay users and ads will work
\item[What is the worst competitive advantage?]
  technological advances (because it quickly disappears)
\item[What is the best competitive advantage?]
  getting something into minds of billions of people that influence their behavior (Coke and Pepsi)
\item[What are the two biggest data providers?]
  Google and Yahoo - financial data different but they both add up to the same number (Goldman Sachs);
  more reliable to go to Goldman Sachs' website (be skeptical about the inaccuracies of the data);
\item[Homework: Figure out what Goldman Sachs does?]
  world's leading financial firm in terms of sophistication
\item[What is the problem with data in finance?]
  non-stationarity; can't project past into future;
  conflicts with sample size (go as far back as you can)
\item[Assumptions]
  every asset's return depends in a linear fashion on a set of systematic factors, also has idiosyncratic (not related to factors) volatility;
  sensitivities to factors differ across assets and are reasonably constant over time;
\item[What risk is diversifiable and what is not?]
  the idiosyncratic risk is diversifiable;
  the systematic risk which depends on beta is undiversifiable
\item[What are possible systematic risks?]
  business cycle - how the economy is doing;
  investor confidence;
  interest rates;
  inflation - short-term unexpected inflation, long-run inflationary expectations
\item[What is the return if all the factors are 0?]
  risk free rate
\item[What happens if you have two different portfolios such that every factor has equal weight but they have different return?]
  arbitrage;
  to avoid arbitrage, expected returns have to have certain form
\item[What are two forms of the Arbitrage Pricing Theory?]
  CAPM and Fama-French 3 Factor model;
  316 factors have been published as significant
\item[What is the objective of companies?]
  maximize value for shareholders
\item[What is the Business Judgement Rule?]
  court accepts what the business is doing is appropriate unless it is too far-fetched
\item[What is a firm?]
  corporate charter and nexus of contracts that defines the firms;
  management (board of directors, e.g. Al Gore for Apple; select senior management);
  suppliers and distributors;
  partners;
  lenders and bondholders;
  shareholders: residual risk bearers;
  government tax collectors;
  customers;
  non-management employees
\item[Why can't Brad Cornell sell Apple?]
  taxes would be 40\% of \$750,000 since it doubled
  hedge but selling calls;
\item[What does finance look like?]
  savers store in real investment;
  finance is net zero
\item[How did Cornell finance his undertaking in writing a book?]
  a pair of blue jeans(\$40 in Germany but \$500 in Prague) would buy you a hotel room and a nice dinner
\end{description}

\begin{description}
\section{Lecture 2 - 4/13/2016}
\item[What do you need to do fundamental analysis?]
  1. Disagree with market.
  2. Be right.
  3. Market comes to realize you are right.
\item[What is an efficient market?]
  market price reflects all private and public information
\item[Why is the efficient market self contradictory?]
  because no one would do research;
  market must be inefficient enough that the best people can be right and make money
\item[How do you diversify?]
  market portfolio
\item[What did Bill Sharpe discover?]
  active investors and passive investors make the same before costs;
  active investors should make less since they have higher costs
\item[Why did indexes beat stock pickers even over 15 years?]
  because of expenses - duh
\item[What are the two ways to overperform?]
  fundamental analysis or quantitative analysis (The D. E. Shaw  Group managed \$40 billion and beats market consistently; Renaissance Technologies (rentec) even more successful (James Simons))
\subsection{Luck vs Skill - Brent Cahill, Mojo, Nick, Ricky}
\item[Background]
  Is active management worth the cost?
  Is skill present? Data suggests it is. Active portfolios have a few constant over/under performers.
\item[What are the 3 forms of market efficiency?]
  Weak - market uses all past and current information. Past rates don't affect future returns.
  Semi-Strong - Quick reaction to public information
  Strong - Market reflects all public and private performance
\item[How do you solve for luck versus skill?]
  assume performance is skill plus luck;
  assume skill and luck is normally distributed with skill having a variable mean;
  investing performance mostly based on luck
\item[How do you do well on an exam?]
  know a lot or be lucky because you don't know everything - the test might just be in the area you knew;
  $E[S|P=p_{obs}] = \mu_S + \frac{\sigma_S^2}{\sigma_S^2 + \sigma_L^2} (p_{obs} - \mu_S)$
\item[What happens when you buy Tesla?]
  you get rights for future dividends;
  value comes from future dividends;
  take into account time and risk
\item[Why are companies incorporated in Delaware?]
  Corporate Law - judges are sophisticated and experienced in corporate law
\item[What happens to remaining stock when company buys most of a company and merges it in?]
  investors have appraisal right (forgo taking money and file appraisal lawsuit in Delaware - could get more money);
  lawsuit costs \$5-10 million;
  Michael Dell took company back private by meeting with Starlight and buying it back and an appraisal lawsuit was filed
\item[How does Delaware value money?]
  break time into 3 buckets - specific forecasts (management comes up with it and it goes out 5 years);
  transition (5 years - take forecasts and converge linearly to steady state);
  terminal year in 10 years (assumes company in steady state and experiencing constant growth)
\item[Who are active investors buying/selling from?]
  other active investors
\item[What is the upper bound for a steady state company?]
  long-run economic growth (hard to predict short run but can predict long run);
  growth in GDP (nominal and real);
  Hungary - 50\% inflation per day - 1 pengo in 1945 equal to $10^{23}$ in 1946
\item[What are currency reforms?]
  reset value
\item[What determines real growth?]
  population (-1 to 3-4\% (number of hours available to work) and productivity (capital and technology)
\item[How does output increase with capital?]
  output increases a lot at first but then tails off
\item[What is the most important date?]
  1665 - closed Cambridge University because of the plague;
  sent Isaac Newton home;
  date that humanity realizes that there are laws of nature that can be written down mathematically
\item[How much did standard of living improve from 200,000 BC to 5,000 BC?]
  maybe 10 times; tiny rate of growth (no economic growth until after 1665)
\item[What does Stephen Hawking say about 1665?]
  it's like giving a 3 year old a AK47
\item[What is long run inflation forecast?]
  2\%
\item[What is long run population growth forecast?]
  0.5\%
\item[What is long run real growth forecast?]
  2\%
\item[What will be long run growth in GDP?]
  4.5\%
\item[What is the average time copanies are on CRSP?]
  7 years
\item[What is the probability for a randomly selected stock to outperform treasury bills?]
  42\%
\item[What percent of stocks account for most growth in GDP?]
  4\%
\item[How do companies grow?]
  inflation or investment
\item[What is inflation?]
  unit of currency shrinks; today we measure stuff in 2009 US dollar
\item[What is the growth rate of a company?]
  amount reinvested times return on investment (real terms);
  $g = k * r$;
  $k = g/r = 0.0125/0.1125 = 11.1\%$ for a company assuming 1.25\% real growth and 11.25\% return on investment;
  11.25\% WACC (8.75\%) + return (4.5\%) minus inflation (2\%)
\item[What is EBITDA?]
  earnings before taxes, depreciation, and amortization
\item[What is NOPAT?]
  net operating profit after tax (EBIT minus tax)
\item[What is net working capital?]
  accounts payable (source of cash) and accounts receivable (drain of cash)
\item[What is unlevered free cash flow?]
  amount of cash available to investors (NOPAT minus cash needed to grow business)
\item[What is Tesla's free cash flow?]
  negative - doing research, building factories and hiring workers for Model 3 (\$35,000)
\item[What is enterprise value?]
  operating value of the company;
  value of its total operations;
\item[How do you get stock price from enterprise value?]
  subtract debt and add cash
\item[what is the discount rate?]
  8.75\%;
  if growth rate is bigger than discount rate, then transition period is too short
\item[What model was used?]
  Solera management projects
\item[What was the mistake in the DCF analysis?]
  37\% plowback whcih is much larger than 11.1\%
\item[How do you decompose a stock price into its component parts?]
  projects in place \& growth options
\end{description}
\end{document}
